An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/eval.tex
add another element to anomaly table
fix compilation for eval

\begin{table*}[t]
\centering
\caption{Sampled benchmarks for anomaly detection}
\label{table-casestudy}
\begin{tabular}{|l|l|l|l|}
\hline
{\bf ID} & {\bf Problem Description} & {\bf URL} & 
{\bf \app Report}  \\ 
\hline
\hline
1 & MySQL Server has gone away error in Wamp 
& goo.gl/axnezi  
& WARNING: Violated Upper Hampel Rule for

%this way of doing is awful
\\ &  & 
& {\tt max\_allowed\_packet} with value 104857600 
 \\ \hline

2 &  MySQL has abnormally high load for CPU 
& goo.gl/JrRLrR
& WARNING: Violated Upper Hampel Rule for % 
& &  & 
& {\tt sort\_buffer\_size} with value 1048576000 
& & &  & WARNING: Violated Upper Hampel Rule for  
& & &  & {\tt read\_rnd\_buffer\_size} with value 283115520 \\ \hline

>>>>

\begin{table*}[t]
\centering
\caption{Sampled benchmarks for anomaly detection}
\label{table-casestudy}
\begin{tabular}{|l|l|l|l|}
\hline
{\bf ID} & {\bf Problem Description} & {\bf URL} & 
{\bf \app Report}  \\ 
\hline
\hline
1 & MySQL Server has gone away error in Wamp 
& goo.gl/axnezi  
& WARNING: Violated Upper Hampel Rule for 
\\ &  & 
& {\tt max\_allowed\_packet} with value 104857600 
 \\ \hline

2 &  MySQL has abnormally high load for CPU 
& goo.gl/JrRLrR
& WARNING: Violated Upper Hampel Rule for  
\\ & & 
& {\tt sort\_buffer\_size} with value 1048576000 \\
& & & WARNING: Violated Upper Hampel Rule for  
\\ & & 
& {\tt read\_rnd\_buffer\_size} with value 283115520 \\ \hline

3 & User is having performance issues with MySQL 
& goo.gl/34jTB5
& WARNING: Violated Upper Hampel Rule for  
\\ & & 
& {\tt query\_cache\_limit} with value 134217728 \\ \hline
